\documentclass{article}

\begin{document} 
\title{Instructions for preparing the end of quarter research report}
\date{}

\maketitle
\vspace{-5ex}


The report should contain the following sections:
\begin{itemize}
\item {\bf Summary}: This section is a short summary of the rest of the report.
\item {\bf Big Picture}: This section contains the whole problem that the lab is
  attempting to solve. It isn't limited to just your own piece and
  may contain goals that were not yet accomplished.  Pictorial
  representations of how the robots/workstation interact for the
  stated problem would be helpful here.
\item {\bf My Contributions}:  This section details your own
  contribution to the `Big Picture' problem of the previous
  section. This section contains high-level descriptions of the work
  you did.
\item {\bf Preliminaries}: In order to make the report more self-contained, an optional preliminaries section could include introductory theory related to the project.
\item {\bf Methodology}: This section describes the way you solved the
  problems described in the previous section.  This section should
  contain the ideas behind the code you've generated.  Also, pictorial
  representations of how the code works or how multiple pieces of code
  interact would aid your exposition.  This section should make
  reference to specific code you've written (but not include them).
  The referenced code should be well commented.
\item {\bf Tips}: This section describes informative tips you feel
  would be useful to someone picking up your project where you left
  off.  It could include challenges you faced and how you solved
  them or links to resources you found especially helpful with a
  description.
\item {\bf Pitfalls}: This section describes issues/complications that arose that
  you were unable to solve.  It could contain problems arising from
  limitations in ROS/turtlebots or alternate approaches to problems
  that you ended up solving a different way.
\item{\bf Conclusions \& Future Directions}: This section begins by clearly
  defining the progress on the `Big Picture' problem.  After that, it
  should describe what the future work should be.  With one more
  quarter, what would you do?
\end{itemize}

Finally, we can provide feedback for early drafts of the report.

\end{document}